### 2012-02-07 paper.tex
Include changes on paper.tex

\noindent \normalsize{High-quality mass spectrometry of the oscillatory behaviour of CO oxidation on supported Pt-nanoparticles is presented. It is demonstrated that the oscillations can continue self-sustained for several days. It is demonstrated that the oscillations exhibits a well defined frequency which is slowly developing towards lower freqeuncy.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

\footnotetext{\textit{$^{a}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
\footnotetext{\textit{$^{b}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark}}

@@

Because of its industrial importance CO oxidation on transition metal surfaces has been widely studied as both industrial catalyst and as a model system for testing catalytic properties of materials (REF, Ertl?). Despite intensive studies this reaction is still not understood and shows interesting new and interesting features.

It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface. CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{$\mu$-reactors}
Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed from atmosphere by anodic bonding a pyrex lid to the silicon reactor, it is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed directly through to the outlet connected to a pressure controller to control the reactor pressure. The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume. An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement doing operation.

The system is fully automized, allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.

A typical oscillation maesurement is done by mounting a sample in setup directly after cluster deposition and anodic bonding. A typical measurement will involve an initial light-off CO-oxidation measurement, where the temperature is slowly increased up until the sample ignites and achieves full conversion of the CO. At the typical conditions (O:CO ratio of typically $\sim13$ and Pt-coverage of $\sim0.1\%$) lighoff happens around 180$^\circ$C, the ramp is typically continued up to 260$^\circ$C whereafter the temperature is lowered at the same rate as the heating (typically 3$^\circ$C/min). A typical initial treatment is seen in figurefigure~\ref{fgr:initial_treatment} Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp. Sustained oscillations is then achieved by following the same heathing ramp up to a fixed temperature and then the temperature is kept constant for the remaing period of the measurement.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample.}
  \label{fgr:initial_treatment}
\end{figure}

@@

\section{Results}
During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce. In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle. In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations. This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).

The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour. A slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
  \label{fgr:full_oscillation}
\end{figure*}

If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods. In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods. Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days. 
% an example of a single-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on. Towards the end, it is also clearly visible how  oscillations with smaller amplitude are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary, sometimes the smaller oscillations will trigger a full switch, and sometimes it will not, thus introducing more short-period oscillations despite the trend of slower and slower oscillations.
% an example of a two-column figure, remember that the graphics should be included where it is first referenced
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment.}
  \label{fgr:extracts}
\end{figure}

\section{Discussion}
Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles. Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.

>>>>

\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented. The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio. The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.}
%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

@@

\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}

@@

CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams. A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction. Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active (under-coordinated?) sites.

Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure. It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{Reactor setup}
The experiments were performed in silicon-based $\mu$-reactors \cite{Henriksen2009}. The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller to control the reactor pressure. The design ensures that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.

Before any measurements are performed the reactor is pumped by a turbopump minimizing contaminants in the system. When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.

The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume. An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.

The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.

@@

BEMÆRK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). The particles are formed by gas-phase condensation from a ﬂux of platinum atoms that are sputtered from a 99.99\,\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3 mm diameter aperture at one end. Argon gas is ﬂown into the volume around the magnetron at a rate of 10–120 sccm and is pumped away via the aperture so that a local pressure of 0.1–1 mbar is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further reﬁned by a skimmer. The nanoparticle beam is then passed through a quadrupole mass ﬁlter where the ionised fraction (60–80\,\%) of the nanoparticles can be ﬁltered according to their mass-to-charge ratio.

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\,\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating. After the initial lightoff the sample is cooled to room temperature. When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim$7\,s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\,\% conversion. Hereafter the conversion increases linearly with time until approximately 50 \,\% conversion is reached. Shortly after reaching 50 \,\% conversion the sample again ignites and covert all CO to CO$_$2. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}
Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_$2 pressure was observed. At a CO/O$_$2 ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_$2 to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation. After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}. Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time. Hereafter the oscillations is more irregular which is evident from Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is between 45 and 20 minutes.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
  \label{fgr:long_measurement}
\end{figure}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from a four day measurement. Here data from shortly after the initial treatment, after 2800\,min. of oscillation time and after 5900\,min. are shown. After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 day long experiment. The oscillation period become more irregular with time while the on/off ratio remains constant. Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
  \label{fgr:extracts}
\end{figure}

The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time. Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure \ref{fgr:full_oscillation}. A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered. At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 could did produce any oscillations in our system. The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}. The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.

Although a range of different CO/O$_2$ ratios were tried no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system. This is not, however, believed to be a property of the platinum thin film but a property of the small reactor used in this study. This is supported by literature where oscillations have been observed on both extended thin-films \cite{Singh2010} as well as on single crystals \cite{Hendriksen2005} at atmospheric pressure.

Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence hypothesized that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette...

%Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.

The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts} is consistent across all measured samples. The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters. Skriv noget mere her...
